---
output: 
  flexdashboard::flex_dashboard:
    theme: readable
params:
  study: NA
  data1: NA
  data2: NA
---
---
title: "`r paste("Safety Explorer Suite for", params$study)`"
---

```{r}
library(safetyexploreR)
```

AE Explorer {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------

The AE Table is an interactive tool that allows users to dynamically query adverse event (AE) data in real time. Examples and additional documentation are available at the [Rho Graphics Site](http://graphics.rhoworld.com/tools/aeexplorer/).

The AE Table is an open source project built using standard web technology and will run in any modern web browser. The displays created are all dynamically linked to raw adverse event data which allows the tool to work with data from any adverse event coding system. The tool was originally created using Javascript/D3, but has been extended to an R tool as well using HTML Widgets.
 
Row 
-------------------------------------
    
### An example of the AE Explorer using R:

```{r, fig.width=5, fig.height=6}
aeExplorer(data=params$data1)
```

AE Timelines {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------

AE-timelines is a JavaScript library, built using Webcharts ([1](https://github.com/RhoInc/Webcharts), [2](https://github.com/RhoInc/webcharts-wrapper-boilerplate)), that creates an interactive timeline showing when participants experienced Adverse Events in a clinical trial. The chart uses the AdAM Adverse Event data standard by default, but can be customized to use any data set that is one record per adverse event. The widget has been extended to use in R with [HTML widgets](http://www.htmlwidgets.org/).
 
Row 
-------------------------------------
    
### An example of AE Timelines using R:
```{r}
aeTimelines(data=params$data1)
```


Safety Histogram {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------
 
Row 
-------------------------------------

### An example of Safety Histogram using R:
```{r}
safetyHistogram(data=params$data2)
```

Safety Outlier Explorer {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------
 
Row 
-------------------------------------

### An example of Safety Outlier Explorer using R:
```{r}
safetyOutlierExplorer(data=params$data2)
```


Safety Results Over Time {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------
 
Row 
-------------------------------------

### An example of Safety Results Over Time using R:
```{r}
safetyResultsOverTime(data=params$data2)
```


Safety Shift Plot {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------
 
Row 
-------------------------------------

### An example of Safety Shift Plot using R:
```{r}
safetyShiftPlot(data=params$data2)
```
