---
output: 
  flexdashboard::flex_dashboard:
    theme: readable
params:
  study: NA
  text1: NA
  text2: NA
  text3: NA
  text4: NA
  text5: NA
  text6: NA
  data1: NA
  data2: NA
---
---
title: "`r paste("Safety Report: ", params$study)`"
---

```{r}
library(safetyexploreR)
```

AE Explorer {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------

`r paste(params$text1)`
 
Row 
-------------------------------------
    
### An example of the AE Explorer using R:

```{r, fig.width=5, fig.height=6}
aeExplorer(data=params$data1)
```

AE Timelines {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------

`r paste(params$text2)`
 
Row 
-------------------------------------
    
### An example of AE Timelines using R:
```{r}
aeTimelines(data=params$data1)
```


Safety Histogram {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------
 
`r paste(params$text3)` 
 
Row 
-------------------------------------

### An example of Safety Histogram using R:
```{r}
safetyHistogram(data=params$data2)
```

Safety Outlier Explorer {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------

`r paste(params$text4)`

Row 
-------------------------------------

### An example of Safety Outlier Explorer using R:
```{r}
safetyOutlierExplorer(data=params$data2)
```


Safety Results Over Time {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------

`r paste(params$text5)`

Row 
-------------------------------------

### An example of Safety Results Over Time using R:
```{r}
safetyResultsOverTime(data=params$data2)
```


Safety Shift Plot {data-orientation=rows}
=========================================

Column {.sidebar data-width=250}
-------------------------------------
 
`r paste(params$text6)`

Row 
-------------------------------------

### An example of Safety Shift Plot using R:
```{r}
safetyShiftPlot(data=params$data2)
```
